---
title: "Weight of Fish"
author: "Candice Fallon"
date: "Spring 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
Allfish <- read.csv(file = "Fish.csv")
Allfish$Species <- as.factor(Allfish$Species)
levels(Allfish$Species)
```

```{r}
Perch <- subset(Allfish, Species == "Perch")
Perch <- select(Perch, -Species)
```


# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  


# Perch

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
From the plot above we see that the two best regression model is height and width. The model of height and width are the adjusted $r^2$ of about 0.9400.
  
##Which is best??  

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[2,]
```

```{r}
Perchmodel <- lm(Weight~Height+Width, data=Perch)
summary.lm(Perchmodel)
```

Here we get that the adjusted $r^2$ is 0.9400 which is the best model because $r^2$ is the highest. The residual standard error is 85.17.

# Bream

# Smelt

